Hybrid platforms and bargaining power

### 2022-12-14 src/paper/application.tex
Start working on bargaining outcomes

Notice that, as each producer is infinitesimal, its pricing decision does not affect the aggregate $A$.
It follows that the profit maximizing price is a simple additive markup over marginal cost
\begin{align*}
    p^*_{Ti} = c_T + \mu,
\end{align*}
and the optimal profit is
\begin{align*}
    \pi^{v*}_{Ti} = \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}.
\end{align*}

@@

% Note that, although the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it.
% TODO: intuition

@@

>>>>

Notice that, as each producer is infinitesimal, its pricing decision does not affect the aggregate $A$.
It follows that the profit maximizing price is a simple additive markup over marginal cost
\begin{align*}
    p^*_{Ti} = c_T + \mu,
\end{align*}
and the optimal profit is
\begin{align}
    \pi^{v*}_{Ti} = \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}.
    \label{eq:optimal_profit}
\end{align}

@@

Note, that even though the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it.
As a consequence, the size of the aggregate, and hence consumer welfare is also unaffected by the platform operating in hybrid mode.
% TODO: intuition
% TODO: when does switching to retail mode occur?

@@

Now consider the case when instead of the platform setting take it or leave it entry fees, it must negotiate with the fringe about the division of profits.
In this case, the timing is slightly different, as the platform cannot commit to an entry fee in the first period.
Instead, the game starts by fringe firms' investment decisions.
After that, in the second period, bargaining takes place between the platform and the fringe firms that have entered the market.

The participants negotiate over the aggregate profits that they can achieve in the subsequent period (assuming non-collusive, monopolistic pricing, as before).
I assume that bargaining outcomes are the Shapley values of the participants, where the value of a coalition is defined as the total profits that the coalition can achieve by selling their products.
As the platform is necessary to reach the customers, the value of any coalition that does not include the platform is zero.
Furthermore, using equation \eqref{eq:variable_profit}, the value of a coalition with $n$ fringe firms and the platform is
\begin{align*}
    v(n) = \mu \frac{n \exp \left( \frac{v_F - c_F - \mu}{\mu} \right) + N_P \exp \left( \frac{v_P - c_P - \mu}{\mu} \right)}{n \exp \left( \frac{v_F - c_F - \mu}{\mu} \right) + N_P \exp \left( \frac{v_P - c_P - \mu}{\mu} \right) + 1}.
\end{align*}

Proposition \ref{prop:one_sided} gives a simple formula for the Shapley value of the platform in case $N_F$ fringe firms made the initial investment:
\begin{align*}
    \pi^t_P &= \varphi_P = \int_0^1 v(tN_F) \dt \\
            &= TODO.
\end{align*}
Subsequently, the fringe gets the remainder of the profits, therefore
\begin{align*}
    \pi^t_F &= \varphi_F =  1 - \int_0^1 v(tN_F) \dt \\
            &= TODO.
\end{align*}
